### 2018-10-23 Latex/article.tex
Article compiled with a Makefile (without figure).
Change width in Latex to equivalent in inches
Update Erik's files

\usepackage{color}
\usepackage{soul}

\pdfoptionpdfminorversion 4

@@

\newcommand{\eps}{\varepsilon}

@@

\newlength{\halfwidth}
\setlength{\halfwidth}{66mm}

@@

\title[Wave energy cascade in shallow-water flows]%
{Wave energy cascade in forced-dissipative one-layer shallow-water flows}

\author[P. Augier and E. Lindborg]%
{Pierre Augier$^{1,2}$%
  \thanks{Email address for correspondence: p.augier@damtp.cam.ac.uk},\ns
and Erik Lindborg$^1$}

\affiliation{$^1$Linn\'e Flow Centre, KTH Mechanics,
SE-100 44 Stockholm, Sweden\\[\affilskip]
$^2$Department of Applied Mathematics and Theoretical Physics,
University of Cambridge, Cambridge CB3 0WA, United Kingdom}

@@

% \baselineskip 8mm
\begin{abstract}
The dynamics of one-layer shallow-water flows forced in medium-scale
wave modes and dissipation acting at small scales is investigated by
means of theoretical analysis and numerical simulations with
resolutions up to $7680^2$.
%
We first focus on the non-rotating case for which a statistically
stationary regime is obtained for all resolutions and Froude numbers
$F_f = \eps/(k_f c)$, where $\eps$ is the energy dissipation rate,
$k_f$ the forcing wave number and $c$ the wave speed.
%
All the injected energy goes into a downscale energy
cascade. Consequently, the spectral energy flux is constant and
positive between the forcing wave number and the wave numbers where
dissipation is active.  The spectral energy flux is exactly
equipartioned between kinetic and potential energy.  An exact third
order structure function law of Kolmogorov type is derived and
numerically verified.  However, the downscale cascade is less
efficient than in three-dimensional Navier-Stokes turbulence, since
the mean energy of the statistically stationary flow scales as
$\sqrt{\eps c /k_f}$ and varies with the dissipative scale.
%
Moreover, the spectra scale as $k^{-2}$ and the structure functions of
order larger than two scale approximately as $r$.
%
%
This intermittent scaling is explained by a simple model based on the
assumption that the statistics is totally determined by shocks.
%
It is verified that the dynamics is not drastically modified by system
rotation as long as the forcing wave number is larger than the
deformation wave number $k_d = f/c$, where $f$ is the Coriolis
parameter.
\end{abstract}

@@

The shallow-water models have been widely used to study basic
mechanisms occurring in geophysical flows \cite[see for
example][]{VallisLIVRE2006}.
%
These models are based on the hydrostatic approximation which is
extremely well satisfied for a very wide range of scales in the oceans
and in the atmosphere \Add{and on which are based the so-called
primitive equations}.  They also rely on a stronger hypothesis
regarding the density stratification.  The fluid is assumed to be
structured in a limited number of thin homogeneous layers, which leads
to equations involving only two-dimensional operators. \Add{However,
as long as there is no overturning, the shallow-water model in the
limit of a large number of layers and the primitive equations describe
the same dynamics. In the opposite limit, two models are particularly
important from the theoretical point of view.} The two-layer
shallow-water model captures the baroclinic instability which is of
primary importance for the dynamics of the oceans and of the
atmosphere \cite[]{VallisLIVRE2006, Wirth2013}.
%
The equations of the one-layer shallow-water model are very similar to
the two-dimensional compressible Navier-Stokes equations.  The
one-layer model does not capture the baroclinic instability but it is
one of the simplest hydrodynamic models with coexisting eigenmodes of
the linearized operator with zero linear frequency and with finite
non-zero linear frequency, $\omega = \pm \omega_l = \pm\sqrt{f^2 + c^2
k^2}$, where $f$ is the Coriolis parameter, $c$ the wave speed and $k
= |\kk|$ the wave number.
%

For geophysical applications, it is convenient to consider the limits
for which the linear frequency $\omega_{l}$ is much larger than the
characteristic nonlinear frequency $\omega_{nl} = U k$, where $U$ is a
characteristic velocity.  In the limit $f/\omega_{nl} \sim
ck/\omega_{nl} \rightarrow \infty$, one can obtain a quasi-geostrophic
one-layer shallow-water model, i.e. derive self-consistent evolution
equations for the 0-linear-frequency variable, the Charney potential
vorticity.  In this limit, the dynamics of the 0-linear-frequency
variable is totally decorrelated from the fast waves.
%
For finite rotation and wave speed, there are slow balanced motions,
which are associated with relatively weak non-zero linear frequency
modes.
%
When $\omega_{nl}(k) \ll \omega_{l}(k) $, there is only a weak
interaction between waves and the balanced modes.
%
Due to its relative simplicity, the one-layer shallow-water model has
been used to study issues like the projection on the balanced manifold
\cite[]{Lorenz1980, MohebalhojehDritschel2000} and the production of
waves by balanced flows \cite[]{FargeSadourny1989,
LahayeZeitlin2012,Vanneste2013}. \Add{In this study, we consider the
same model in order to address a related but different issue.}

Balanced flows have a dynamics which is very similar to
two-dimensional turbulence.
%
In the quasi-geostrophic limit, the space-averaged energy and the
space-averaged potential enstrophy are conserved, positive definite
and proportional in Fourier space. This leads\Add{, as in
two-dimensional turbulence,} to an upscale energy cascade and a
downscale enstrophy cascade.
%
Thus, the small-scale dissipation vanishes in the limit of zero
viscosity.
%
In contrast to this, statistical mechanics indicates that wave energy
should be transferred towards small scales \cite[]{Warn1986}.
Numerical simulations have shown that long waves lose their energy by
transferring it to shorter waves \cite[]{Sadourny1975,
FargeSadourny1989, YuanHamilton1994}.  The mechanism of a wave cascade
has been proposed to explain the attraction towards the balanced flows
\cite[]{Sadourny1975}.  \cite{YuanHamilton1994} showed that
statistically stationary shallow-water flows can be obtained forcing
quasi-geostrophic modes at large scales and with dissipation only at
small scales.
%
\Add{They propose that the $k^{-5/3}$ spectra that are observed at the
atmospheric meso-scales} \cite[]{NastromGage1985, FrehlichSharman2010}
\Add{and reproduced by some atmospheric models based on the primitive
equations} \cite[]{KoshykHamilton2001, Skamarock2004,
Hamilton_etal2008} \Add{could be reproduced by the one-layer
shallow-water model by a downscale energy cascade of waves.}

However, few studies have investigated the dynamics of the downscale
energy cascade of waves in shallow-water models.
%
Most numerical studies have investigated decaying flows and have not
focused on the cascade \cite[]{FargeSadourny1989,
LarichevMcWilliams1991, SpallMcWilliams1992,
PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012}.
%
Moreover, there are strong discrepancies between different numerical
results and between these results and available theoretical results.
%
\cite{FargeSadourny1989} reported spectra scaling like $k^{-4}$
whereas those shown by \cite{LahayeZeitlin2012} scale like $k^{-6}$.

Some predictions are based on the weak wave turbulence formalism
\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011}.  In the case of
inertial-gravity waves, \cite{FalkovichMedvedev1992} showed that the
exact solutions of the kinetic equation corresponding to a constant
downscale energy flux is associated with a spectrum scaling like $E(k)
\sim P^{2/3} k^{-8/3}$.
%
However, as pointed out by \cite{FalkovichMeyer1996} when the
dispersion is small enough, waves moving in the same direction have
the same velocity and interact strongly, which can lead to the
formation of shocks. \Add{In this case, the weak wave turbulence
formalism is unable to give valuable results.}  Such sharp and long
structures have been observed in many simulations
\cite[]{FargeSadourny1989, PolvaniMcWilliamsSpallFord1994,
LahayeZeitlin2012} but \Add{their effects} are not well understood.
%
\cite{Kuznetsov2004} predicted that a flow dominated by shocks should
be associated with spectra scaling like $E(k) \sim k^{-2}$.
%
\cite{FalkovichMeyer1996} simulated acoustic turbulence dominated by shocks 
and reported spectra in agreement with this theoretical prediction.
%
The shocks also lead to very strong intermittency, as demonstrated by
\cite{BouchaudMezardParisi1995} and \cite{WeinanKhaninMazelSinai1997}
in the case of Burgers turbulence.
%

The dynamics of waves in complex shallow-water flows is not well
understood.  \Add{Our long-term goal is to understand this dynamics
which involves interactions between balance and unbalance parts of the
flow. However, even the wave cascade without balance flow is not well
understood.} A statistically stationary wave cascade has never been
simulated at high resolution.
%
Is it possible to obtain a statistically stationary state in the very
fast wave regime, and how does the mean energy in this hypothetical
regime depends on the forcing and the wave speed?  
% What is the slope of 
\Add{How does} the energy spectra \Add{scale as a function of the
input parameters}?
%
All these questions are open and straightforward simulations may
provide the answers.

\cite{YuanHamilton1994} and \cite{FalkovichMeyer1996} carried out
forced dissipated simulation of the one-layer shallow water model and
acoustic turbulence, respectively.
% 
However, the resolution in both studies was quite coarse \Add{($386^2$
and $101^2$ grid points, respectively)} so that the inertial range was very
narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
type of strongly anisotropic forcing \Add{with waves in only one
direction} while \cite{YuanHamilton1994} forced in geostrophic modes
which severely complicates the interpretation.

In this paper, we investigate the dynamics of one-layer shallow-water
flows forced in the wave modes by means of high resolution numerical
simulations \Add{with up the  $7680^2$ grid points}.
%
The model is described in section~\ref{section_basic_theory}.
%
We then derive some new theoretical results for this model and for
turbulence dominated by shocks
(section~\ref{section_advanced_theory}).
%
The numerical methods and the forcing are described in
section~\ref{section_methods}.
%
The main numerical results corresponding to the simple case without
global rotation are presented in
section~\ref{section_wave_cascade_f=0}.
%
We investigate the sensibility of the non-rotating results to a
moderate rotation (section~\ref{section_rotation}).

\section{The one-layer shallow-water model}
\label{section_basic_theory}
% \input{section_basic_theory}

\section{Theoretical analysis}
\label{section_advanced_theory}
% \input{section_advanced_theory}

\section{Numerical methods}
\label{section_methods}
% \input{section_methods}

\section{Wave cascade without global rotation}
\label{section_wave_cascade_f=0}
% \input{section_wave_cascade_f=0}

\section{Effects of global rotation}
\label{section_rotation}
% \input{section_rotation}

>>>>

\usepackage{color}
\usepackage{soul}
\usepackage{booktabs}
\pdfoptionpdfminorversion 4

@@

@@

\newlength{\halfwidth}
\setlength{\halfwidth}{2.6in}

@@

\title[Shallow water wave turbulence]%
{ Shallow water wave turbulence}

\author[P. Augier, A.V. Mohanan and E. Lindborg]%
{Pierre Augier$^{1}$,   A. V. Mohanan$^{2}$
and Erik Lindborg$^2$ \ns }

\affiliation{$^2$ KTH Mechanics,
SE-100 44 Stockholm, Sweden\\[\affilskip]
$^1$ LEGI, BP53,
38041 Grenoble Cedex, France}

@@

% \baselineskip 8mm

\begin{abstract}

The dynamics of irrotational shallow water wave turbulence forced in large
scales and dissipated at small scales is investigated. First, we derive the
shallow water analogue of the `four-fifths law' of Kolmogorov turbulence
for a third order structure function involving velocity and displacement
increments. Using this relation and assuming that the flow is dominated by
shocks we develop a simple model predicting that the shock amplitude scales as
$ (\epsilon d)^{1/3} $, where $ \epsilon $ is the mean dissipation rate and $ d $
the mean distance between the shocks, and that the $ p $:th order displacement
and velocity structure functions scale as $ (\epsilon d)^{p/3} r/d $, where $ r $
is the separation. Then we carry out a series of forced simulations with
resolutions up to $7680^2$, varying the Froude number, $F_{f} = \epsilon^{1/3} /
ck_f^{1/3} $, where $ k_f $ is the forcing wave number and $c$ is the wave
speed. In all simulations a stationary state is reached in which there is a
constant spectral energy flux and equipartition between kinetic and potential
energy in the constant flux range. The third order structure function relation
is satisfied with a high degree of accuracy. Mean energy is found to scale as $
E \sim \sqrt{\epsilon c/k_f} $, and is also dependent on resolution, indicating
that shallow water wave turbulence does not fit into the paradigm of a
Richardson-Kolmogorov cascade. In all simulations shocks develop, displayed as
long thin bands of negative divergence in flow visualisations. The mean
distance between the shocks is found to scale as $ d \sim F_f^{1/2}/k_f $.
Structure functions of second and higher order are found to scale in good
agreement with the model. We conclude that in the weak limit, $ F_f \rightarrow
0 $, shocks will become denser and weaker and finally disappear for a finite
Reynolds number. On the other hand, for a given $ F_{f} $, no matter how small,
shocks will prevail if the Reynolds number is sufficiently large.

\end{abstract}

@@

The shallow water (SW) equations  have been widely used to study basic
mechanisms occurring in geophysical flows \cite[see for
example][]{VallisLIVRE2006}.
%
The equations are based on the hydrostatic approximation which is
extremely well satisfied for a very wide range of scales in the oceans
and in the atmosphere.  They also rely on a stronger hypothesis
regarding the density stratification.  The fluid is assumed to be
structured in a limited number of thin homogeneous layers, which leads
to equations involving only two-dimensional operators. The two-layer
SW equations capture the baroclinic instability which is of
primary importance for the dynamics of the oceans and of the
atmosphere \cite[]{VallisLIVRE2006, Wirth2013}.
%
The single layer SW equations are very similar to
the two-dimensional compressible Navier-Stokes equations.  The
equations do not capture baroclinic instability but they constitute
one of the simplest hydrodynamic models with coexisting eigenmodes of
the linearized operator with zero linear frequency and with finite
non-zero linear frequency, $\omega = \pm\sqrt{f^2 + c^2
k^2}$, where $f$ is the Coriolis parameter, $c$ the gravity wave speed and $k
= |\kk|$ the wave number.
%

For geophysical applications, it is convenient to consider the limit
for which the linear wave frequency  is much larger than the
characteristic nonlinear frequency $ U k$, where $U$ is a
characteristic velocity.  In this limit, one can obtain a quasi-geostrophic
single layer SW model, i.e. derive self-consistent evolution
equations for a zero frequency variable, the Charney potential
vorticity, which is totally decoupled from the fast waves.
%
For finite rotation and wave speed, there are slow balanced motions,
which are associated with relatively weak non-zero linear frequency
modes and there is only a weak
interaction between waves and the balanced motions.
%
Due to their relative simplicity, the SW equations have
been used to study issues like the projection on the balanced manifold
\cite[]{Lorenz1980, MohebalhojehDritschel2000} and the production of
waves by balanced flows \cite[]{FargeSadourny1989,
LahayeZeitlin2012,Vanneste2013}.
In this study, we consider the
same equations in order to address a related but different issue.

Balanced flows have a dynamics which is very similar to
two-dimensional turbulence, with an upscale energy cascade. %
Small scale energy dissipation vanishes in the limit of zero
viscosity.
%
In contrast to this, statistical mechanics indicates that wave energy
should be transferred towards small scales \cite[]{Warn1986}.
Numerical simulations have shown that long waves lose their energy by
transferring it to shorter waves \cite[]{Sadourny1975,
FargeSadourny1989, YuanHamilton1994}.  The mechanism of a wave cascade
has been proposed to explain the attraction towards the balanced flows
\cite[]{Sadourny1975}.  \cite{YuanHamilton1994} showed that
statistically stationary shallow-water flows can be obtained forcing
quasi-geostrophic modes at large scales and with dissipation only at
small scales.
%
They propose that the $k^{-5/3}$ spectra that are observed at the
atmospheric meso-scales  \cite[]{NastromGage1985,LiLindborg2018}
and reproduced by some atmospheric models based on the primitive
equations \cite[]{KoshykHamilton2001, Skamarock2004,
Hamilton_etal2008} could be reproduced by the one-layer
shallow-water model by a downscale energy cascade of waves.
However, few studies have investigated the dynamics of the downscale
energy cascade of waves in SW models.
Most numerical studies have investigated decaying flows and have not
focused on the cascade \cite[]{FargeSadourny1989,
LarichevMcWilliams1991, SpallMcWilliams1992,
PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012}.
%
Moreover, there are strong discrepancies between different numerical
results and between these results and available theoretical results.
%
\cite{FargeSadourny1989} reported spectra scaling as $k^{-4}$
whereas those shown by \cite{LahayeZeitlin2012} scale as $k^{-6}$.

Some predictions are based on the weak wave turbulence formalism
\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011}. In the case of
inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the exact
solutions of the kinetic equation corresponding to a constant downscale energy
flux is associated with a spectrum scaling as $E(k) \sim k^{-8/3}$, while
\cite{ZakharovSagdeev1970} used weak turbulence formalism to derive a spectrum
of the form $ E(k) \sim k^{-3/2} $ for acoustic turbulence. This prediction is
of particular interest, since the acoustic equations and the SW equations are
identical when a first order expansion is made in density or displacement
perturbations. It may be questioned, however, that weak turbulence formalism is
applicable to acoustic and SW wave turbulence, no matter how weak the
nonlinearities are supposed to be. As pointed out by \cite{KadomtsevPet1970}
and \cite{FalkovichMeyer1996}, when dispersion is small enough, waves moving in
the same direction have the same velocity and interact strongly, which leads to
the formation of shocks. In this case, the weak wave turbulence formalism is
unable to give valuable results. Such sharp and long structures have been
observed in many simulations \cite[]{FargeSadourny1989,
PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012} but their effects are not
well understood.
%
As shown by \cite{Burgers1948} the energy spectrum of a flow dominated by
shocks will scale as $ k^{-2} $, a prediction which has been confirmed by a
great number of simulations of Burgers equation \cite[for a review, see ]
[]{Frisch2001}. The shocks also lead to very strong intermittency, as
demonstrated by \cite{BouchaudMezardParisi1995} and
\cite{WeinanKhaninMazelSinai1997} for Burgers turbulence.
%
\cite{FalkovichMeyer1996} simulated acoustic turbulence dominated by shocks
and reported spectra scaling as $ k^{-2} $.
\cite{YuanHamilton1994} carried out
forced dissipative simulations of the SW equations showing similar spectra.
However, the resolution in both these studies was quite coarse, ($386^2$
and $101^2$ grid points, respectively) so that the scaling range was very
narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
type of strongly anisotropic forcing with waves in only one
direction while \cite{YuanHamilton1994} forced in geostrophic modes
which severely complicates the interpretation.

The dynamics of waves in complex SW flows is not well
understood.  Even wave dynamics in absence of a balanced flow is not well
understood. A statistically stationary wave cascade has never been
simulated at high resolutions.
%
Is it possible to obtain a statistically stationary state in the very
fast wave regime, and how does the mean energy in this hypothetical
regime depends on the forcing and the wave speed?
% What is the slope of
How do energy spectra scale with the input parameters? From a theoretical point
of view, the most interesting issue is, perhaps, the nature of the dynamics in
the limit of weak nonlinearities. Will shocks prevail in this limit?
%
Such questions are still open and straightforward simulations may
provide the answers.
In this paper, we investigate the dynamics of single layer SW wave turbulence
forced  at large scales by means of
simulations with up the  $7680^2$ grid points.
%
Before presenting the results of the simulations we develop some theory.
%

\section{Theory}

In a non-rotating system of reference the SW equations for a thin layer of fluid over a flat bottom and with a free
surface can be written as  \cite[see for example][]{VallisLIVRE2006}
\begin{eqnarray} \label{UEq}
\p_t \uu + \uu\cdot \bnabla  \uu   
&=& - c^2 \bnabla h + \frac{\nu}{h}  \bnabla^2 \uu,   \label{eq_uu}\\ \label{HEq}
\p_t   h    &=& - \bnabla \cdot (h \uu).  \label{eq_h}
\end{eqnarray}
where $\uu$ is the horizontal velocity, %
$h = 1 + \eta $ the non-dimensional thickness of the fluid layer,  $ \eta $ being the surface displacement, 
$\nu$ the kinematic viscosity and $ c $ is the gravity wave speed. The SW equations conserve mass, $ h $, and momentum $ {\bf J} = h{\bf u} $. As a matter of fact, we have constructed the viscous term in (\ref{UEq}) in such a way that momentum is conserved and energy dissipation is positive definite. This can only be accomplished by permitting the term to be nonlinear in the flow variables. There are different forms of nonlinear terms that fulfil both conditions and it may be disputed which is the best one. However, in the simulations we will use diffusion terms in both (\ref{UEq}) and (\ref{HEq}) that will not fulfil any of these two conditions in a strict sense and we will therefore not discuss this matter further. The inviscid SW equations conserve a local
quantity along trajectories of the fluid particles, the Ertel
potential vorticity $\ErtelPV = \zeta /h$, where $\zeta  $ is the vorticity, which in a rotating system should be interpreted as absolute vorticity.  This conservation law will be of no relevance in the present study in which we only consider
irrotational flows for which the velocity can be written as $ \uu = \bnabla \phi $ , where $ \phi $ is the velocity potential. In a domain with no net fluxes through the boundaries the inviscid equations conserve energy, $ E = E_K + E_P $, where $ E_K =   {\bf J}  \cdot {\uu} /2 $ is kinetic energy and $ E_P = c^{2} h^2/2 $ is potential energy. The latter can be split into three terms as \begin{equation}
E_P = c^2/2 + c^2\eta+ c^2 \eta^2/2, 
\end{equation}
where the first term corresponds to the potential energy of a state with no
surface displacement.  The third term, which is quadratic in the surface displacement, may be named available potential energy (APE),
$E_A = c^2\eta^2/2$, a concept introduced by  \cite{Lorenz1955}. As a consequence of mass and energy conservation the SW equations also conserve the sum of kinetic and available potential energy, $ E_K + E_A $.
 The velocity potential and the displacement of the linearised inviscid SW equations both satisfy the wave equation,
\begin{equation}
\frac{\partial ^2 \eta}{\partial t^2} = c^2 \nabla^2 \eta \, ,
\end{equation}
with equipartition between KE and APE over a wave period in each Fourier mode.

In order to analyze the spectral flux of energy, we derive the spectral energy
budget, i.e.\ the governing equations for spectral KE and APE
functions. This is not as straightforward as in incompressible turbulence since
the expression of the kinetic energy  is not
quadratic. To define the spectral KE function, we use the relation
\begin{equation}
\mean { E_K } = \sum_\kk \scalarprod{\uu}{\JJ}/2,
\end{equation}
where
\begin{equation}
\scalarprod{\baa}{\bb} \equiv \Re\{ \hat \baa(\kk)^* \cdot \hat \bb(\kk) \},
\end{equation}
and $\Re$ denotes the real part, $\kk$ is the wave number and the
hat denotes the Fourier transform.
%
The spectral KE function can therefore be defined as
\begin{equation}
E_K(\kk) \equiv \scalarprod{\uu}{\JJ}/2.
\end{equation}
Similarly, the APE can be written as the sum over all wave numbers of
the spectral APE function 
\begin{equation}
E_A(\kk) =  c^2 \scalarprod{\eta}{\eta}/2 \, .
\end{equation}
The inviscid equation for the spectral KE and APE functions can be written as
\begin{eqnarray}
\p_t E_K(\kk) &=& T_K(\kk) - C (\kk),\\
\p_t E_A(\kk) &=& T_A(\kk) + C (\kk),
\end{eqnarray}
where
\begin{equation}
T_K(\kk) 
= -\scalarprod{\bnabla \cdot \uu}{E_K} 
-\scalarprod{\uu }{\bnabla E_K } \, ,
\end{equation}
\begin{equation}
T_A(\kk) = -c^2 \scalarprod{\bnabla \eta }{\JJ}- c^2\scalarprod{\eta}{\bnabla \cdot \JJ}  \, ,
\end{equation}
are the spectral transfer functions of KE and APE, respectively, and
\begin{equation}
C (\kk) 
= \scalarprod{\uu}{\bnabla E_P}
\end{equation}
is the spectral KE-APE conversion function.
The spectral energy flux functions of KE and APE are defined as
\begin{eqnarray}
\Pi_K (k) = \sum_{| {\bf k}^{\prime} | > k} T_K ( {\bf k}^\prime ) \, , \;\;\;  \Pi_A (k) = \sum_{| {\bf k}^{\prime} | > k} T_A ( {\bf k}^\prime ) 
\end{eqnarray}

We will now derive an analogue of the so called `four-fifths  law' \cite[]{Kolmogorov1941} for the the third order velocity structure function of incompressible isotropic turbulence.   In the case of irrotational SW wave turbulence the analogous law contains a third order structure function involving both velocity and displacement increments.  In order for such a law to exist it is necessary that the velocity field is either non-divergent (incompressible) or irrotational. To derive the law it is convenient to start from the following equations
\begin{eqnarray} \label{IRR}
\p_t \uu &=& -\bnabla \cdot (\uu \cdot \uu /2) - c^2 \bnabla h  \\
\p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
\p_t h   &=& -\bnabla \cdot \JJ \, ,
\end{eqnarray}
where we have used the  assumption that the velocity field is irrotational in (\ref{IRR}). We consider two points, positioned at $ \bf x $ and $ {\bf x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
Using Cartesian tensor notation we denote derivates with respect to $ {\bf x} $ as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $ \partial^{\prime}_i $. Treating $ \bf x $ and $ {\bf x}^\prime $ as independent variables we find

\begin{equation}
\p_t ( J_i' u_i ) = - \p_i( J_i'|\uu|^2/2) - \p_i'(u_j J_j' u_i')
-\p_i (J_i' c^2 h)  - \p_i' (u_i E_p')
\end{equation}
and
\begin{equation}
\p_t ( h' h ) = - \p_i( h'J_i ) - \p_i'( hJ_i' ),
\end{equation}
which gives
\begin{eqnarray}
\p_t ( \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h )
&=& - \p_i( J_i'|\uu|^2/2) - \p_i'( J_i|\uu'|^2/2) %\nonumber \\&& 
- \p_i'(u_j J_j' u_i') - \p_i(u_j' J_j u_i) \nonumber\\
&& -c^2\p_i (J_i'h) - c^2\p_i' (J_ih') %\nonumber\\&& 
- \p_i' (u_i E_p') - \p_i (u_i' E_p) \nonumber\\
&& -2c^2\p_i' (J_i'h) - 2c^2\p_i (J_ih').
\end{eqnarray}
We then assume homogeneity and take the average denoted by
$\meane{}$.   For
every function $g(\xx, \xx')$, we have $\p_i' \meane{g} =
-\p_i\meane{g} = \bnabla_{\rr} \meane{g}|_i$. We thus obtain
\begin{eqnarray}
\p_t \meane{ \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h }
&=& + \bnabla_{\rr}\cdot\meane{ \JJ'|\uu|^2/2 - \JJ|\uu'|^2/2 } \nonumber\\
&& - \bnabla_{\rr}\cdot\meane{ u_j J_j' \uu' - u_j' J_j \uu } \nonumber\\
&& - \bnabla_{\rr}\cdot\meane{ \uu E_p'- \uu' E_p } \nonumber\\
&& -c^2\bnabla_{\rr}\cdot\meane{ \JJ'h - \JJ h' }
\end{eqnarray}
%
We then introduce the structure functions and the operator $\delta$
returning the increment of a variable between two points separated by $\rr$, 
for example $\delta h (\xx, \rr) = h(\xx+\rr)- h(\xx)$.
%
Using homogeneity again, we obtain
\begin{equation}
\meane{ (\delta h)^2 \delta\uu } = 
-\meane{ h'^2 \uu } + \meane{ h^2 \uu' }
+2\meane{ hh' \uu } - 2\meane{ hh' \uu' }
\end{equation}
and 
\begin{equation}
\meane{ |\delta \uu|^2 \delta\JJ } = 
\meane{  |\uu|^2 \JJ' } - \meane{ |\uu'|^2\JJ }
+\meane{ u_ju_j' \JJ' } - \meane{  u_ju_j' \JJ },
\end{equation}
which gives
\begin{equation}
2\p_t \meane{ \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h }
= \bnabla_{\rr} \cdot ( \meane{ |\delta \uu|^2 \delta\JJ } 
+ c^2\meane{ (\delta h)^2 \delta\uu } ).
\end{equation}
For separations that are considerably larger than dissipative scales of motion and considerably smaller than forcing scales a standard argument \cite[see for example][]{Frisch} gives that the left hand side is approximately equal to $ -8 \epsilon $, where $ \epsilon $ is the mean dissipation rate. It is interesting to note that a factor of $ 8 $ appears in the case when the velocity field is irrotational while a corresponding factor of $ 4 $ appears in the case when the velocity field is non-divergent. 
Assuming isotropy and integrating yield the Kolmogorov law for
irrotational shallow water wave  turbulence
\begin{equation}
\meane{ |\delta \uu|^2 \delta J_L } 
+ c^2\meane{ (\delta h)^2 \delta u_L } = -4 \epsilon r, \label{eq_Kolmo}
\end{equation}
where $J_L \equiv
\JJ\cdot\rr / |\rr|$ and $u_L \equiv \uu\cdot\rr / |\rr|$ are
longitudinal increments.

We will now use (\ref{eq_Kolmo}) together with straightforward geometrical and statistical arguments to construct a model for velocity and displacement structure functions of any order above a certain minimum.
The model has some similarities with the one developed by \cite{BouchaudMezardParisi1995} for Burgers equation. The main difference is the that the mean dissipation rate, $\epsilon $, enters into the estimate of the shock amplitude and the final expressions of the structure functions in our model, but is absent in the model of \cite{BouchaudMezardParisi1995}.
We consider a domain with total area  $ {\mA} $ occupied by shocks which we 
consider as smooth lines. We denote the total length of all shocks by $ L_s $.  The mean distance between the shocks within the domain can be estimated as
\begin{equation}
d \simeq \frac{\mA} {L_s} .
\end{equation} 
A structure function of a flow variable is defined as the area average of increments  between two points separated by a distance $ r $.
Assuming that the contribution from increments where the two points are not separated by a shock is negligible for higher order structure functions we obtain
\begin{eqnarray}
\meane{|\delta h|^p} 
=  \frac{1}{\mA} \int_{\mA}  d^2\xx |\delta h(\xx)|^p 
 \simeq  \frac{r}{\mA} \int_\shocks ds |\sin\theta| |\Delta h (s)|^p,
\end{eqnarray}
where $\theta$ is the angle between the shock line and the separation
vector $\rr$ %
and $\Delta h (s)$ is the shock displacement amplitude.
%
Assuming isotropy, the integral can be split and we get
\begin{equation} \label{StepH}
\meane{|\delta h|^p} 
\simeq 
r \frac{L_s}{\mA} \meant{|\sin\theta|} \means{|\Delta h |^p}
\simeq  \frac{2}{\pi} \means{|\Delta h |^p} \frac{r}{d} ,
\end{equation}
where $\meant{}$ is the mean over $\theta$
and $\means{}$ is the mean over all shocks.

For velocity increments, we can also use a characteristic of the
velocity singularities.  The step in velocity is only in the component
perpendicular to the shocks, which implies that the longitudinal and
transverse increments can be written as  $\delta u_L = \delta u
\sin\theta$, $\delta u_T = \delta u \cos\theta$.
%
Applying the same averaging method, we obtain
\begin{equation} \label{StepL}
\meane{|\delta u_L|^p} 
\simeq 
\meant{|\sin\theta|^{1+p}}
\means{|\Delta u |^p} \frac{r}{d}
\end{equation}
and
\begin{equation} \label{StepT} 
\meane{|\delta u_T|^p} 
\simeq 
\meant{|\sin\theta||\cos\theta|^{p}}
\means{|\Delta u |^p} \frac{r}{d},
\end{equation}
where $\Delta u $ is the shock velocity amplitude.
%
These assumptions completely determine the ratio between the
longitudinal and transverse structure functions, which can be computed as
\begin{eqnarray} \label{Ratio}
R_p(r) \equiv \frac{\meane{|\delta u_L|^p}}{\meane{|\delta u_T|^p}} = 
\frac{\meant{|\sin\theta|^{1+p}}}{\meant{|\sin\theta||\cos\theta|^p}},
\end{eqnarray}
giving the numerical values $R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$.
Interestingly, for an isotropic and irrotational velocity field, the longitudinal and transverse second order structure functions
are exactly related by $\meane{(\delta u_L)^2} = \p_r( r\meane{(\delta
u_T)^2} )$ \cite[]{Lindborg2007jas}. If we further assume than both second order structure functions follow
the same scaling law $\meane{ (\delta u_L)^2} \propto \meane{ (\delta
u_T)^2} \propto r^\alpha$, then we have $\meane{ (\delta u_L)^2} =
(1+\alpha) \meane{ (\delta u_T)^2} $, which gives $ R_2 = 2 $ for 
$  \alpha = 1$.  In the limit $ r \rightarrow 0 $ we have $ \alpha = 2 $ and $ R_2 = 3 $.
%

In order for (\ref{StepH}-\ref{StepT}) to match with the third order structure function law (\ref{eq_Kolmo})  the shock amplitudes should scale as
\begin{equation} \label{Strength}
 | \Delta u | \sim | c \Delta h | \sim (\epsilon d)^{1/3} \, ,
\end{equation} 
and the structure functions of order $ p $ will consequently scale as
\begin{equation} \label{StrucFunc}
\meane{|\delta u |^p}  \sim \meane{(c|\delta h |)^p} \sim  (\epsilon  d)^{p/3} \,  \frac{r}{d} \, .
\end{equation} 
Assuming that (\ref{StrucFunc}) is valid for second order moments and that the non-quadratic contribution to the KE spectrum is negligible the corresponding scaling law for the energy spectra reads
\begin{equation} \label{Spectra}
E_K(k)  \sim  E_A(k) \sim \epsilon ^{2/3} d^{-1/3} k^{-2} \, .
\end{equation} 
The  model  provides the following predictions for the flatness factors of velocity increments
\begin{eqnarray} \label{FL}
F_L &=&  \frac{\meane{|\delta u_L|^4}}{\meane{|\delta u_L|^2}^2}
\propto 
\frac{\meant{|\sin\theta|^5}}{\meant{|\sin\theta|^3}^2} \frac{d}{r}   = \frac{9\pi}{15}  \frac{d}{r} \\ \label{FT}
F_T &=&  \frac{\meane{|\delta u_T|^4}}{\meane{|\delta u_T|^2}^2} 
\propto
\frac{\meant{|\sin\theta||\cos\theta|^4}}{\meant{|\sin\theta||\cos\theta|^2}^2} =  \frac{9\pi}{10}  \frac{d}{r} 
\end{eqnarray}
The ratio between the two flatness factors is equal  to
$F_T/F_L = 3/2$ according to the model.
